\documentclass[english]{article}

% Imported Packages
%------------------------------------------------------------------------------
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{extarrows}
\usepackage{setspace}
\usepackage{babel}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{tabulary}
\usepackage[pageanchor]{hyperref}
%------------------------------------------------------------------------------

% For Graphs
%------------------------------------------------------------------------------
\usepackage{tikz}
\usepackage{verbatim}
\usetikzlibrary{positioning,arrows,shapes}

% Header and Footer
%------------------------------------------------------------------------------
\pagestyle{plain}  
\renewcommand\headrulewidth{0.4pt}                                      
\renewcommand\footrulewidth{0.4pt}                                    
%------------------------------------------------------------------------------


% Document
%------------------------------------------------------------------------------
\begin{document}

% Title Page & Table of Contents
%------------------------------------------------------------------------------
\pagenumbering{gobble} 
\vspace*{\fill} 
\centering{
\LARGE{SFWR ENG 3A04 Project}\\
\smallskip
\Large{Deliverable 1}\\
\bigskip \bigskip \bigskip
\Large{
Group 10\\
\medskip
\begin{tabular}{l l}
    Amanda Boudreau & 0344130\\
    Jordan Floyd & 1225123\\
    Mario Machado & 1211979\\
    Rakesh Mistry & 1221428\\
    Ali Reda & 1206754\\
\end{tabular}\\
}
\bigskip \bigskip \bigskip
\today
}
\vspace*{\fill} 

\newpage

\tableofcontents

\newpage

\pagenumbering{arabic}
\setcounter{page}{1}
\raggedright

\section{Introduction}
\label{sec:introduction}
% Begin Section

\subsection{Purpose}
\label{sub:purpose}
% Begin SubSection	
This document will describe what our product intends to accomplish, what its assumptions are, and what it relies on. Anyone with a non-technical background will still be able to read and understand how the \textbf{Application} will work on a higher level after reading this requirements specification document.
% End SubSection

\subsection{Scope}
\label{sub:scope}
% Begin SubSection
\begin{enumerate}[a)]
	\item \textbf{Cabpool} shall be an  \textbf{Android} \textbf{Application} produced for an unidentified taxi company to be used in conjunction with their \textbf{Dispatcher} system with the aim of increasing the volume of taxi users.  
	\item The software shall provide a platform for taxi users to carpool and reduce individual fare cost without requiring the sharing of personal contact information.
	\item The software shall provide the \textbf{User} with Offer Taxi Mode and Request Taxi Mode. Within each mode the \textbf{User} shall be able to accept or reject any search result based on distance, rating and fare price.
	\item The software shall serve as a social networking service to connect users who want to travel to similar locations. As well, the \textbf{User} of the software shall be able to invite fellow users to their \textbf{\emph{Friends List}} and share contact information with one another. Conversely, users will be able to add other users to a \textbf{\emph{Blacklist}} to ensure they never share a cab with that \textbf{User} again. 
	\item The software shall not provide personal information without express permission in accordance with the Ontario Freedom of Information and Privacy Act and the Personal Information Protection and Electronic Documents Act. 
	\item The software will interface with \textbf{Google Maps} to enable users to view their route and potential route changes.
	\end{enumerate}
% End SubSection

\subsection{Definitions, Acronyms, and Abbreviations}
\label{sub:definitions_acronyms_and_abbreviations}
% Begin SubSection
\begin{enumerate}
	\item  \textbf{Android} - the  \textbf{Android} mobile operating system.
	\item \textbf{Application} - for the purposes of this SRS, \textbf{Application} and app refer to a mobile application.
	\item \textbf{\emph{Blacklist}} - a list of users who will no longer be able to share a cab.
	\item \textbf{Cabpool} - the name of our app.
	\item \textbf{Confirmation Code} - a string of 4-8 characters to be delivered via text.
	\item \textbf{Dispatcher} - the system co-ordinating and keeping track of where users are who are offering/requesting a cab.
	\item \textbf{\emph{Friends List}} - a list of users who will be able to see more information about this \textbf{User} and easily share cabs.
	\item \textbf{GPS} - Global Positioning System, an accurate worldwide navigational and surveying facility based on the reception of signals from an array of orbiting satellites.
	\item \textbf{Google Maps} - an online mapping solution which can show user's locations using GPS.
	\item \textbf{Google Play} - the  \textbf{Android} App Store which this app will be launched on.
	\item \textbf{Legal} - the viewpoint of the law.
	\item \textbf{Security} - the viewpoint of all things \textbf{Security} and encryption related.
	\item \textbf{Splash Screen} - a screen with the app's logo on it, used for loading.
	\item \textbf{User} - the person(s) using the app.
\end{enumerate}
% End SubSection

\subsection{References}
\label{sub:references}
% Begin SubSection
All references to privacy laws throughout the SRS are from the following document:
\begin{enumerate}
	\item Freedom of Information and Protection of Privacy Act, R.S.O. 1990, CHAPTER F.31, \url{http://www.e-laws.gov.on.ca/html/statutes/english/elaws_statutes_90f31_e.htm}
\end{enumerate}

% End SubSection

\subsection{Overview}
\label{sub:overview}
% Begin SubSection
The remaining sections of this document provide a general description of \textbf{Cabpool}, including a description of its users. It also includes the product's innovative features, functional requirements, and non-functional requirements. A general description of the project is discussed in Section 2 of this document. Section 3 gives the functional requirements such as constraints and assumptions made while designing the application. It also explores the product from various viewpoints. Section 4 details the non-functional requirements of the application, discussing the external interface requirements and other usability and performance-related requirements.
% End SubSection

% End Section

\section{Overall Description}
\label{sec:overall_description}
% Begin Section

\subsection{Product Perspective}
\label{sub:product_perspective}
% Begin SubSection
Two notably similar applications already exist in the \textbf{Google Play} store, however, there are some key differences between those products and ours. One of the existing applications only attempts to make it easier for friends or strangers to carpool with their personal vehicles, not using a taxi service. The second product uses a taxi service, but customers who share a taxi must be picked up, and dropped off at the same destination. Our product uses a taxi service, thus eliminating risk of illegal activities that may occur when carpooling with a stranger, and does not limit carpoolers to having the exact same pick-up and destination locations.
\\
\bigskip
Our \textbf{Application} is intended to be used as a sub-component of the taxi company dispatching system. The company dispatching system requires filling any taxi requests. Our \textbf{Application} will allow users to offer a taxi up for sharing. When this happens, the dispatching system will be notified of a taxi that may be able to fill another taxi request. Information such as the taxi's current location, and destination will be passed. Users are also able to request a shared taxi. When this request is filed, the dispatching system is again notified, so it may try to match a shared taxi offer with a shared taxi request. Matches will only be made if the users will save money choosing to share, as opposed to requesting a new taxi, and not sharing. If one match or more is made, the \textbf{User} who initiated the request may view which taxis they may take in order to save money. Information about each taxi ride will be shown to the user. The \textbf{User} may then submit a final request for the specific taxi chosen in the viewable list. The \textbf{User} that offered that taxi will be notified of a potential carpooler, and will have the choice to accept or decline the request.
% End SubSection

\subsection{Product Functions}
\label{sub:product_functions}
% Begin SubSection
\begin{enumerate}[a)]
	\item The \textbf{Application} will enable users to create a profile and enter two modes, Request Taxi Carpool and Offer Taxi Carpool. In the Offer Taxi Carpool mode the \textbf{User} will scan a barcode within the taxi which will contain taxi identification information to be sent to the Dispatcher. In each mode the \textbf{User} will be able to enter their destination and sort their search results by distance, ratings and fare price. 
	
	\item The \textbf{User} will be able to enter constraint criteria such as preferred sex and maximum number of passengers. When a match is selected a request is sent to the \textbf{Dispatcher} which will relay the request for confirmation from the potential match. 
	
	\item The \textbf{Dispatcher} will store all taxi and \textbf{User} information to enable users to connect with one another, sharing taxis and reducing fares without releasing personal information to strangers. The \textbf{Application} will ensure that all messages will retain confidentiality and integrity.
	
	\item The \textbf{Application} will display the fare owed by each customer and allow rating of customers with whom the ride was shared. Additionally, customers will be able to add other riders to a \textbf{\emph{Friends List}} or a \textbf{\emph{Blacklist}}.
	
	\item The \textbf{Application} will enable customers to view their route on Google Maps, as well as any potential route changes.
\end{enumerate}
% End SubSection

\subsection{User Characteristics}
\label{sub:user_characteristics}
% Begin SubSection
We expect two different type users using this application: 
\begin{itemize}
    \item users \textit{requesting} a taxi
    \item users \textit{offering} a taxi
\end{itemize}
The \textbf{User} must to be over the age of eighteen for \textbf{Legal} reasons. The \textbf{User} is expected to be English literate and be able to navigate through an application. The \textbf{Application} will have options to input personal information, destinations, schedules, etc. Therefore the \textbf{User} must be capable of understanding what the \textbf{Application} is doing.
\\
\bigskip
The \textbf{User} will not be expected to have technical expertise or high education, as the \textbf{Application} will be built to be \textbf{User} friendly to the general public. Since the expected users will be carpooling many times, the \textbf{User} is encouraged to be social to make rides more pleasant for both type of users. 
% End SubSection

\subsection{Constraints}
\label{sub:constraints}
% Begin SubSection
The successful completion of this project will be contingent upon our ability to work within the following contstraints:
\begin{enumerate}
	\item The \textbf{Application} must be developed for the  \textbf{Android} mobile operating system
	\item The \textbf{Application} must be built and submitted before the final deadline of December 3rd, 2014
\end{enumerate}
% End SubSection

\subsection{Assumptions and Dependencies}
\label{sub:assumptions_and_dependencies}
% Begin SubSection
This Software Requirements Specification document makes the following assumptions:
\begin{enumerate}
	\item The software does not need to provide directions for the driver of the taxi. If it is necessary that the taxi driver should receive directions to customers the SRS will have to be modified.
	\item The  \textbf{Android} operating system will be available on the hardware for which the software is designed.
	\item The taxi company has a regular method of sending out taxis in addition to the sharing service. If the app is to be the only way to call a cab the SRS will need to be modified with this in mind.
	\item Although the fare will be displayed on the app, the payment transactions are not completed within the app. 
	\item The \textbf{Google Maps} API will be available, as it will be needed to fulfill many of the requirements.
\end{enumerate}
% End SubSection

\subsection{Apportioning of Requirements}
\label{sub:apportioning_of_requirements}
% Begin SubSection
Requirements pertaining to capacity, size, and speed will not be considered for this version of the system but may need to be considered if the system is to work with large volumes of consumers in later versions. 
% End SubSection

% End Section

\section{Functional Requirements}
\label{sec:functional_requirements}

% Begin Section:
\begin{enumerate}[{BE}1.]
	\item Application is Opened
	\begin{enumerate}[{VP1}.1]
		\item User
			\begin{enumerate}
				\item \textbf{User} views \textbf{Splash Screen} followed by main menu upon loading.
				\item \textbf{User} will automatically log in using stored data from previous session.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item \textbf{Dispatcher} will be notified of \textbf{User} log in. 
			\end{enumerate}
		\item Security
			\begin{enumerate}
			\item \textbf{User} information will be sent securely.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
			\item VOID
			\end{enumerate}
	\end{enumerate}

	\item New Account Sign Up is Initiated	
	\begin{enumerate}[{VP2}.1]
		\item User
			\begin{enumerate}
				\item \textbf{User} is prompted to create a unique username, set a password, enter their date of birth, and enter their phone number.
				\item If a unique username is chosen and the \textbf{User} is over 18, the \textbf{User} will be taken to a new screen asking for their \textbf{Confirmation Code} (which was sent via text to the phone number they entered).
				\item Once the correct \textbf{Confirmation Code} is entered, the \textbf{User} is taken to the main screen of the app, containing options to offer or request a cab. 
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item Verify that a unique username has been chosen by the user, and that the \textbf{User} is over the age of 18.
				\item Send a \textbf{Confirmation Code} via text to the user's specified phone number.
				\item Verify that the \textbf{Confirmation Code} entered by the \textbf{User} matches the one sent via text.
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item All information encrypted and kept confidential within the app.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item All information is secure and not shown to anyone but user, unless \textbf{User} gives permission.
			\end{enumerate}
	\end{enumerate}

	\item Login is Initiated
	\begin{enumerate}[{VP3}.1]
		\item User
			\begin{enumerate}
				\item Sees form where username and password can be given as input.
				\item Sees the main menu screen if login was successful and is asked to try again if the login was unsuccessful.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item \textbf{Dispatcher} is notified that the \textbf{User} is online.
				\item Receives users information and must verify that the \textbf{User} has an account and has input the correct password.
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item \textbf{User} information must be encrypted so that third parties cannot intercept the users password, which would grant them access to personal information.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item All information is kept secure and not shown to anyone but \textbf{User}, unless \textbf{User} gives permission.
			\end{enumerate}
	\end{enumerate}

	\item Modify Account Tab is Opened	
	\begin{enumerate}[{VP4}.1]
		\item User
			\begin{enumerate}
				\item The \textbf{User} sees the “Modify” button.
				\item The \textbf{User} selects what needs modifying, and views options of what he can modify.
				\item The \textbf{User} clicks “Save” and his selection is saved. The Modify function is over, and the app goes back to the previous page.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item VOID
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item All information encrypted and kept confidential within the app.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item All information is kept secure and not shown to anyone but \textbf{User}, unless \textbf{User} gives permission.
			\end{enumerate}
	\end{enumerate}

	\item Offer	Mode is Initiated	
	\begin{enumerate}[{VP5}.1]
		\item User
			\begin{enumerate}
				\item \textbf{User} must scan a QR code inside the cab to initiate the offer process.
				\item \textbf{User} is notified when a request is made, and must either accept or decline the request.
				\item Once the \textbf{User} has arrived at their final destination they shall see the amount they owe the taxi driver and are given the chance to rate the other customer (if a request was made and accepted).
				\item The \textbf{User} will have the chance to add the other customer to their \textbf{\emph{Friends List}} or add them to their \textbf{\emph{Blacklist}}.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item Receives the user's information and sends them the information connected to the relevant offers.
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item \textbf{User} information must be encrypted so that third parties cannot intercept the users current or target destinations.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item All information is kept secure and not shown to anyone but \textbf{User}, unless \textbf{User} gives permission.
			\end{enumerate}
	\end{enumerate}

	\item Request Mode is Initiated	
	\begin{enumerate}[{VP6}.1]
		\item User
			\begin{enumerate}
				\item \textbf{User} sees form where request time, request destination, and target destination can be taken as input. \textbf{User} must see a list of available offers. 
				\item Once an offer is selected the \textbf{User} shall receive more information and have the option to accept the offer. 
				\item Once the \textbf{User} has arrived at their final destination they shall see the amount they owe the taxi driver and are given the chance to rate the other customer. 
				\item The \textbf{User} will have the chance to add the other customer to their \textbf{\emph{Friends List}} or add them to their \textbf{\emph{Blacklist}}. 
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item Receives the users information and sends them the information connected to the relevant offers.
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item \textbf{User} information must be encrypted so that third parties cannot intercept the users current or target destinations.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item All information is kept secure and not shown to anyone but \textbf{User}, unless \textbf{User} gives permission.
			\end{enumerate}
	\end{enumerate}
	
	\item Cancel Taxi Request/Offer
	\begin{enumerate}[{VP7}.1]
		\item User
			\begin{enumerate}
				\item The offer/request made is removed from viewable list of pending offer/requests.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item The cancelled offer/request from this \textbf{User} must be removed from the system.
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item The cancelled offer/request signal must be sent to \textbf{Dispatcher} in a secure manner.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item VOID
			\end{enumerate}
	\end{enumerate}
	
	\item Send Friend Request
	\begin{enumerate}[{VP8}.1]
		\item User
			\begin{enumerate}
				\item Allow users to accept or decline friend requests.
				\item Show friend request pending if the request has not yet been accepted.
				\item Remove friend request pending if the friend request is declined.
				\item Add the friend to \textbf{\emph{Friends List}} of both users once the request is accepted, and remove friend request pending.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item VOID
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item Allow profile information to be shared between friends confidentially.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item On the very first occurrence, notify the \textbf{User} that profile information will be shared between friends.
			\end{enumerate}
	\end{enumerate}
	
	\item Remove Friend
	\begin{enumerate}[{VP9}.1]
		\item User
			\begin{enumerate}
				\item Allow users to remove friends from \textbf{\emph{Friends List}}.
				\item The removed friend will no longer be in the users \textbf{\emph{Friends List}}.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item VOID
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item Profile information of both users will no longer be viewable.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item On the very first occurrence, notify the \textbf{User} that removed friend's profile will no longer be accessed.
			\end{enumerate}
	\end{enumerate}

	\item Add User to \textbf{\emph{Blacklist}}
	\begin{enumerate}[{VP10}.1]
		\item User
			\begin{enumerate}
				\item User can enter the username of another user or select a user from the list of people they've recently shared a cab with whom they wish to add to their \textbf{\emph{Blacklist}}.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item VOID
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item Blacklisted user will no longer be able to send/receieve offers/requests to/from the \textbf{User} who added them to their \textbf{\emph{Blacklist}}.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item On the very first occurrence, notify the \textbf{User} that the Blacklisted user will no longer be able to share a cab with them.
			\end{enumerate}
	\end{enumerate}

	\item Remove User from \textbf{\emph{Blacklist}}
	\begin{enumerate}[{VP11}.1]
		\item User
			\begin{enumerate}
				\item User selects a user they wish to remore from their \textbf{\emph{Blacklist}}.
				\item Selected user is no longer visible on their \textbf{\emph{Blacklist}}.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item VOID
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item Un-Blacklisted user will now be able to send/receieve offers/requests to/from the \textbf{User} who added them to their \textbf{\emph{Blacklist}}.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item On the very first occurrence, notify the \textbf{User} that the Un-Blacklisted user will now be able to share a cab with them.
			\end{enumerate}
	\end{enumerate}
	
	\item Preferences Tab is Opened
	\begin{enumerate}[{VP12}.1]
		\item User
		\begin{enumerate}
			\item The \textbf{User} views the “preferences” button.
			\item The \textbf{User} views his options and can input his favorite locations to go to.
			\item The \textbf{User} can allow other users to see his frequent locations.
		\end{enumerate}
		\item Dispatcher
		\begin{enumerate}
			\item VOID
			 \dots
		\end{enumerate}
		\item Security
		\begin{enumerate}
			\item All information kept secure within the app.
			\item Favorite locations only shown if \textbf{User} allows it.
		\end{enumerate}
		\item Legal
		\begin{enumerate}
			\item All information is encrypted and kept confidential and not shown to anyone but user, unless \textbf{User} gives permission.
		\end{enumerate}
	\end{enumerate}
	
	\item Logout is Initiated
	\begin{enumerate}[{VP13}.1]
		\item User
			\begin{enumerate}
				\item Any offers/requests made must be canceled.
				\item  \textbf{Android} \textbf{Application} will return to main screen.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item Any offers/requests from this \textbf{User} must be removed from the system.
				\item Location information of the \textbf{User} is no longer accessible.
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item Logout signal must be sent securely to dispatcher.
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item Information on the user's current location must not be accessible by any third parties including friends.
			\end{enumerate}
	\end{enumerate}

	\item Application is Closed
	\begin{enumerate}[{VP14}.1]
		\item User
			\begin{enumerate}
				\item The  \textbf{Android} \textbf{Application} will close and be off screen.
				\item The  \textbf{Android} \textbf{Application} will minimize mobile resources used.
				\item Any offers/requests made will not be canceled.
			\end{enumerate}
		\item Dispatcher
			\begin{enumerate}
				\item VOID
			\end{enumerate}
		\item Security
			\begin{enumerate}
				\item VOID
			\end{enumerate}
		\item Legal
			\begin{enumerate}
				\item VOID
			\end{enumerate}
	\end{enumerate}

\end{enumerate}

% End Section

\section{Non-Functional Requirements}
\label{sec:non-functional_requirements}
% Begin Section
\subsection{Look and Feel Requirements}
\label{sub:look_and_feel_requirements}
% Begin SubSection

\subsubsection{Appearance Requirements}
\label{ssub:appearance_requirements}
% Begin SubSubSection
\begin{enumerate}[{AR}1. ]
	\item The \textbf{Application} shall provide a satellite image of the users destination and location and all surroundings using \textbf{GPS} capabilities.
	\item The \textbf{Application} must show a splash page when \textbf{User} first enters the application.
	\item The \textbf{Application} will be bright and colorful rather than dark and plain. Use uniform colors.
\end{enumerate}
% End SubSubSection

\subsubsection{Style Requirements}
\label{ssub:style_requirements}
% Begin SubSubSection
\begin{enumerate}[{SR}1. ]
	\item The \textbf{Application} shall provide a uniform look and feel between all the pages and tabs.
	\item The \textbf{Application} must show all buttons, tabs, pages clear to user. Avoid messiness.
	\item The \textbf{Application} must feel smooth to user. Avoid long loading times. 
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Usability and Humanity Requirements}
\label{sub:usability_and_humanity_requirements}
% Begin SubSection

\subsubsection{Ease of Use Requirements}
\label{ssub:ease_of_use_requirements}
% Begin SubSubSection
\begin{enumerate}[{EUR}1. ]
	\item The \textbf{Application} must be usable with one hand, for users who are on the go.
	\item The Offer and Request process must be simple, requiring no more than 3 steps to complete.
\end{enumerate}
% End SubSubSection

\subsubsection{Personalization and Internationalization Requirements}
\label{ssub:personalization_and_internationalization_requirements}
% Begin SubSubSection
\begin{enumerate}[{PIR}1. ]
	\item Users shall be able to personalize their experience under the Preferences tab, setting things like their preferred gender to cab with.
\end{enumerate}
% End SubSubSection

\subsubsection{Learning Requirements}
\label{ssub:learning_requirements}
% Begin SubSubSection
\begin{enumerate}[{LR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Understandability and Politeness Requirements}
\label{ssub:understandability_and_politeness_requirements}
% Begin SubSubSection
\begin{enumerate}[{UPR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Accessibility Requirements}
\label{ssub:accessibility_requirements}
% Begin SubSubSection
\begin{enumerate}[{ACR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Performance Requirements}
\label{sub:performance_requirements}
% Begin SubSection

\subsubsection{Speed and Latency Requirements}
\label{ssub:speed_and_latency_requirements}
% Begin SubSubSection
\begin{enumerate}[{SLR}1. ]
	\item Load times between screens shall be no longer than 2 seconds, to provide the \textbf{User} with a seamless experience.
\end{enumerate}
% End SubSubSection

\subsubsection{Safety-Critical Requirements}
\label{ssub:safety_critical_requirements}
% Begin SubSubSection
\begin{enumerate}[{SCR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Precision or Accuracy Requirements}
\label{ssub:precision_or_accuracy_requirements}
% Begin SubSubSection
\begin{enumerate}[{PAR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Reliability and Availability Requirements}
\label{ssub:reliability_and_availability_requirements}
% Begin SubSubSection
\begin{enumerate}[{RAR}1. ]
	\item The system must be available at all times of the day which the taxi company operates.
\end{enumerate}
% End SubSubSection

\subsubsection{Robustness or Fault-Tolerance Requirements}
\label{ssub:robustness_or_fault_tolerance_requirements}
% Begin SubSubSection
\begin{enumerate}[{RFR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Capacity Requirements}
\label{ssub:capacity_requirements}
% Begin SubSubSection
\begin{enumerate}[{CR}1. ]
	\item The system must be able to handle 20 to 30 users at one time. 
\end{enumerate}
% End SubSubSection

\subsubsection{Scalability or Extensibility Requirements}
\label{ssub:scalability_or_extensibility_requirements}
% Begin SubSubSection
\begin{enumerate}[{SER}1. ]
	\item The system shall be designed in such a manner that it would be able to support more users and taxi companies with minimal upgrades and modifications.
\end{enumerate}
% End SubSubSection

\subsubsection{Longevity Requirements}
\label{ssub:longevity_requirements}
% Begin SubSubSection
\begin{enumerate}[{LONGR}1. ]
	\item The system shall last as long as the current version of the  \textbf{Android} OS is supported.
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Operational and Environmental Requirements}
\label{sub:operational_and_environmental_requirements}
% Begin SubSection

\subsubsection{Expected Physical Environment}
\label{ssub:expected_physical_environment}
% Begin SubSubSection
\begin{enumerate}[{EPE}1. ]
	\item The \textbf{Application} will have simple graphical interfaces to allow for ease of use when travelling outdoors.
	\item The \textbf{Application} will run on  \textbf{Android} smartphones.
\end{enumerate}
% End SubSubSection

\subsubsection{Requirements for Interfacing with Adjacent Systems}
\label{ssub:requirements_for_interfacing_with_adjacent_systems}
% Begin SubSubSection
\begin{enumerate}[{RIAS}1. ]
	\item The \textbf{Application} will interface with \textbf{Google Maps} and Facebook.
\end{enumerate}
% End SubSubSection

\subsubsection{Productization Requirements}
\label{ssub:productization_requirements}
% Begin SubSubSection
\begin{enumerate}[{PR}1. ]
	\item Initially the system will work for a small number of taxis and users. Prior to completion this will be increased to reflect an expected expanded \textbf{User} base.
\end{enumerate}
% End SubSubSection

\subsubsection{Release Requirements}
\label{ssub:release_requirements}
% Begin SubSubSection
\begin{enumerate}[{RR}1. ]
	\item The \textbf{Application} will be available for download and install through \textbf{Google Play} \textbf{Application} store.
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Maintainability and Support Requirements}
\label{sub:maintainability_and_support_requirements}
% Begin SubSection

\subsubsection{Maintenance Requirements}
\label{ssub:maintenance_requirements}
% Begin SubSubSection
\begin{enumerate}[{MR}1. ]
	\item The system should be documented in such a way that maintaining and updating it is easy for users who did not build it initially.
\end{enumerate}
% End SubSubSection

\subsubsection{Supportability Requirements}
\label{ssub:supportability_requirements}
% Begin SubSubSection
\begin{enumerate}[{MSR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Adaptability Requirements}
\label{ssub:adaptability_requirements}
\begin{enumerate}[{MAR}1. ]
	\item The system should be built in such a way that adding entirely new features does not require the rewriting of old features. 
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Security Requirements}
\label{sub:security_requirements}
% Begin SubSection

\subsubsection{Access Requirements}
\label{ssub:access_requirements}
% Begin SubSubSection
\begin{enumerate}[{SAR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Integrity Requirements}
\label{ssub:integrity_requirements}
\begin{enumerate}[{SIR}1. ]
	\item The system shall encrypt all it's data before sending it between the \textbf{Application} and the dispatcher. 
\end{enumerate}
% End SubSubSection

\subsubsection{Privacy Requirements}
\label{ssub:privacy_requirements}
\begin{enumerate}[{SPR}1. ]
	\item The system shall protect the privacy of users, not allowing users to access others users personal.
\end{enumerate}
% End SubSubSection

\subsubsection{Audit Requirements}
\label{ssub:audit_requirements}
% Begin SubSubSection
\begin{enumerate}[{SAUR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

\subsubsection{Immunity Requirements}
\label{ssub:immunity_requirements}
% Begin SubSubSection
\begin{enumerate}[{SIMR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Cultural and Political Requirements}
\label{sub:cultural_and_political_requirements}
% Begin SubSection

\subsubsection{Cultural Requirements}
\label{ssub:cultural_requirements}
% Begin SubSubSection
\begin{enumerate}[{CCR}1. ]
	\item The product will use British spelling.
\end{enumerate}
% End SubSubSection

\subsubsection{Political Requirements}
\label{ssub:political_requirements}
% Begin SubSubSection
\begin{enumerate}[{CPR}1. ]
	\item This \textbf{Application} will work with the taxi cab company that commissioned it only.
\end{enumerate}
% End SubSubSection

% End SubSection

\subsection{Legal Requirements}
\label{sub:legal_requirements}
% Begin SubSection

\subsubsection{Compliance Requirements}
\label{ssub:compliance_requirements}
% Begin SubSubSection
\begin{enumerate}[{LCR}1. ]
	\item This product will comply with the Personal Information Protection and Electronic Documents Act.
	\item This product will comply with the Ontario Freedom of Information and Privacy Act.
\end{enumerate}
% End SubSubSection

\subsubsection{Standards Requirements}
\label{ssub:standards_requirements}
% Begin SubSubSection
\begin{enumerate}[{LSR}1. ]
	\item VOID
\end{enumerate}
% End SubSubSection

% End SubSection

% End Section
\newpage
\appendix
\section{Division of Labour}
\label{sec:division_of_labour}
% Begin Section
In order to complete this document, all work was divided equally. Each group member did the same amount of work as the other, no more, no less. By signing below, we hereby acknowledge that the work was in fact divided equally.\\
\bigskip
\begin{tabular}{l l}
Amanda Boudreau & \line(1,0){50}\\
Jordan Floyd & \line(1,0){50}\\
Mario Machado & \line(1,0){50}\\
Rakesh Mistry & \line(1,0){50}\\
Ali Reda & \line(1,0){50}\\
\end{tabular}

% End Section

\end{document}
%------------------------------------------------------------------------------
